---
title: "Imputation"
author: "Peng Chen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Imputation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview


__StatComp20037__ is a simple R package developed to view and imputate the missing data. Two functions are considered, namely, _miss.view_ (view the missing data in barplot or heatplot form) and _miss.imp_ (imputate the missing data in the data matrix with differents methods including mean, median and linear regression). 


## _miss.view_ and _miss.imp_


The source R code for _miss.view_ is as follows:
```{r}

#view the missing data
miss.view <- function(data, type='bar'){
  if (type == 'bar'){
    miss.num <- apply(is.na(data), 2, sum)
    barplot(miss.num, col='red')
  } else if (type == 'heat') {
    data <- apply(is.na(data), 2, as.numeric)
    heatmap(data,  Rowv = NA, Colv = NA,
            col = colorRampPalette(colors = c("white",'white',"red"))(100))
  } else {
    print('error: the type should be bar or heat')
  }
}
```


The source R code for _miss.imp_ is as follows:
```{r}
##imputate the missing data
miss.imp <- function(data, method='mean'){
  library(stats)
  m <- nrow(data)
  n <- ncol(data)
  #imputate with mean
  if (method == 'mean'){
    for (j in 1:n){
      data[,j][is.na(data[,j])] <- mean(data[,j], na.rm = TRUE)
    }
  }
  # imputate with median
  else if (method == 'median'){
    for (j in 1:n){
      data[,j][is.na(data[,j])] <- median(data[,j], na.rm = TRUE)
    }
  }
  #imputate with reg
  else if (method == 'reg'){
    s <- which(is.na(data)==TRUE) # the place of missing data
    x <- s%%m # the rows of the missing data
    y <- 1 + s %/% m # the columns of the missing data
    
    cor <- cor(data, use = "complete.obs") # correlation between columns
    for (j in 1:n){
      miss.y <- data[,j] #response y of lm
      i <- order(abs(cor[j,]))[n-1]
      miss.x <- data[,i] #variable x of lm
      res <- lm(miss.y~miss.x)
      imp <- res$coefficients[1] + res$coefficients[2]*miss.x
      # imputation with lm prediction
      for (i in 1:m){
        if (is.na(miss.y[i])==TRUE & is.na(imp[i])==TRUE){
          miss.y[i] <- mean(miss.y)
        } else if (is.na(miss.y[i])==TRUE & is.na(imp[i])==FALSE){
          miss.y[i] <- imp[i]
        } else {
          miss.y[i] <- miss.y[i]
        }
      }
      data[,j] <- miss.y
    }
  }
  else {
    data <- 'error: the method should be mean, median or reg'
  }
  return(data)
}
```